CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-04-07 script/en/chapters/aboutcryptool.tex
richard's comments

\parskip 4pt
\vskip + 30 pt
{
In this CrypTool\index{CrypTool} script you will find predominantly
mathematically oriented information on using cryptographic procedures.
The main chapters have been written by {\em various authors} and are
therefore independent from one another. At the end of most chapters
you will find literature and web links.

You will find information about the principles of symmetrical and
asymmetrical {\bf encryption}. A large section of the script is dedicated
to the fascinating topic of {\bf prime numbers}. Using numerous examples,
the {\bf elementary number theory} and {\bf modular arithmetic} are
introduced and applied in an exemplary manner to the {\bf RSA procedure}.
After this, one receives insight into the mathematical ideas behind
{\bf modern cryptography}.

%You will also obtain an overview of the
%mathematical ideas behind modern cryptography.

A further chapter is devoted to {\bf digital signatures}, 
which are an essential component of e-business applications. 
The last chapter describes {\bf elliptic curves}: they could be used
as an alternative to RSA they are extremely well suited for 
implementation on smartcards.

Whereas the program CrypTool\index{CrypTool} teaches you how to use
cryptography in practice, the script provides those interested in the
subject with a deeper understanding of the mathematical algorithms
used -- trying to do it didactically as well as possible.

The {\em authors} Bernhard Esslinger, Matthias B\"uger, Bartol Filipovic, 
Henrik Koy, Roger Oyono and J\"org-Cornelius Schneider
would like to take this opportunity to thank their colleagues 
in the company and at the universities of Frankfurt, Gie\ss en, 
Siegen and Karlsruhe. They particularly thank Dr. Peer Wichmann
from the Karlsruhe computer science research centre
(Forschungszentrum Informatik, FZI) for his down-to-earth support.

\enlargethispage{0.5cm}
As at CrypTool\index{CrypTool}, the quality of the script is enhanced
through your suggestions and ideas for improvement. We look forward 
to your feedback.

\vskip +7 pt \noindent
You will find the current version of CrypTool\index{CrypTool} under \newline
  \href{http://www.cryptool.org}{\texttt{http://www.cryptool.org}},~
  \href{http://www.cryptool.com}{\texttt{http://www.cryptool.com}}~ or~
  \href{http://www.CrypTool.de}{\texttt{http://www.cryptool.de}}.
{
\vskip + 7 pt \noindent
The contact persons for this free open source tool are listed 
in the readme file delivered within the CrypTool\index{CrypTool} package.}
}

>>>>

\parskip 4pt
%\vskip +12 pt
{
\noindent In this CrypTool\index{CrypTool} script you will find predominantly
mathematically oriented information on using cryptographic procedures.
The main chapters have been written by {\em various authors} and are
therefore independent from one another. At the end of most chapters
you will find literature and web links.

You will obtain information about the principles of symmetrical and
asymmetrical {\bf encryption}. A large section of this script is dedicated
to the fascinating topic of {\bf prime numbers}. Using numerous examples,
the {\bf elementary number theory} and {\bf modular arithmetic} are
introduced and applied in an exemplary manner for the {\bf RSA procedure}.
By reading this you'll gain an insight into the mathematical ideas behind
{\bf modern cryptography}.

A further chapter is devoted to {\bf digital signatures}, 
which are an essential component of e-business applications. 
The last chapter describes {\bf elliptic curves}: they could be used
as an alternative to RSA and in addition are extremely well suited for 
implementation on smartcards.

Whereas the \textit{program} CrypTool\index{CrypTool} teaches you how to use
cryptography in practice, the \textit{script} provides those interested in the
subject with a deeper understanding of the mathematical algorithms
used -- trying to do it in an instructive way.

The {\em authors} Bernhard Esslinger, Matthias B\"uger, Bartol Filipovic, 
Henrik Koy, Roger Oyono and J\"org-Cornelius Schneider
would like to take this opportunity to thank their colleagues 
in the company and at the universities of Frankfurt, Gie\ss en, 
Siegen, Karlsruhe and Darmstadt. They are particularly indepted Dr. Peer
Wichmann from the Karlsruhe computer science research centre (Forschungszentrum
Informatik, FZI) for his down-to-earth support and in addition would like to
acknowledge the proof-reading done by Richard Chistiansen and XXXXXX XXXXXXX.

\enlargethispage{12pt}
As at CrypTool\index{CrypTool}, the quality of the script is enhanced
by your suggestions and ideas for improvement. We look forward 
to your feedback.

\vskip +7 pt \noindent
You will find the current version of CrypTool\index{CrypTool} under \newline
  \href{http://www.cryptool.org}{\texttt{http://www.cryptool.org}},~
  \href{http://www.cryptool.com}{\texttt{http://www.cryptool.com}}~ or~
  \href{http://www.CrypTool.de}{\texttt{http://www.cryptool.de}}.

\vskip +7 pt \noindent
The contact people for this free open-source tool are listed 
in the ``readme'' file delivered within the CrypTool\index{CrypTool} package.}

### 2003-04-07 script/en/chapters/cryptomethods.tex
richard's comments

The purpose of encryption \index{Encryption} is to change data in such a way
that only an authorised recipient is able to reconstruct the plaintext. This
has the advantage of being able to transmit encrypted data openly and 
nevertheless need not fear a perpetrator reading the data without 
authorisation. Authorised recipients possess a piece of secret 
information -- called the key -- which allows them to decrypt the data
while it remains hidden from everyone else.\par \vskip + 3pt

One encryption procedure has been proved to be secure -- the {\em One
Time Pad}\index{One ­Time ­Pad}. However, this procedure has several practical
disadvantages (the key used must be selected randomly and must be at least as long
as the message being protected), which means that it is hardly used except in
closed environments such as for the hot wire between Moscow and Washington.\par \vskip + 3pt

@@

The book of Bruce Schneier \cite{Schneier1996cm} offers a very good overview about the different algorithms. We basically distinguish between symmetric and asymmetric encryption procedures.

@@

In their 2001-paper Ferguson, Schroeppel and Whiting \cite{Ferguson2001} presented a new method of symmetric codes cryptanalysis: They described AES with a closed formula (in the form of a continued fraction) which was possible because of the "relatively" clear structure of AES. This formula consists of around 1000 trillion terms of a sum - so it does not help concrete practical cryptanalysis. Nevertheless -curiosity in the academic community awakened. It was already known, that the 128-bit AES could be described as an over-determined system of about 8000 quadratic equations (over an algebraic number field) with about 1600 variables (some of them are the bits of the wanted key) -- equation systems of that size are in practice not solvable. This special equation system is relatively sparse, so only very few of the quadratic terms (there are about 1,280,000 are possible quadratic terms in total) appear in the equation system.

The mathematicians Courois and Pieprzyk \cite{Courtois2002} published a paper in 2002, which got a great deal of attention amongst the crypto community: The pair had further developed the XL-method (eXtended Linearization), introduced at Eurocrypt 2000 by Shamir et al., to create the so called XSL-method (eXtended Sparse Linearization). The XL-method is a heuristic technique, which in some cases manages to solve big non-linear equation systems and which was till then used to analyze an asymmetric algorithm (HFE).  The innovation of Courois and Pieprzyk was, to apply the XL-method on symmetric codes: the XSL-method can be applied to very specific equation systems. A 256-bit AES could be attacked in roughly $2^{230}$ steps. This is still a purely academic attack, but also a direction pointer for a complete class of block ciphers. The major problem with this attack is that until now nobody has worked out, under what conditions it is successful: the authors specify in their paper necessary conditions, but it is not known, which conditions are sufficient.
There are two very new aspects of this attack: firstly this attack is not based on statistics but on algebra. So attacks seem to be possible, where only very small amounts of cipher text are available. Secondly the security of a product-algorithm does not exponentially increase with the number of rounds.

@@

The discussion is very controversial at the moment: Don Coppersmith (one of the inventors of DES) for example queries the practicability of the attack because XLS would provide no solution for AES \cite{Coppersmith2002}. This concludes that then the optimization of Murphy and Robshaw \cite{Robshaw2002b} would not work.

@@

Brute-force (exhaustive search, trial-and-error) means to completely examine all keys of the key space: so no special analysis methods have to be used. Instead, the cipher text is decrypted with all possible keys and for each resulting text it is checked, whether this is a meaningful clear text. A key length of 64 bit means at most $2^{64}$ = 18,446,744,073,709,551,616 or about 18 trillion (GB) / 18 quintillion (US)  keys to check\index{CrypTool}%
\footnote{%
    With CrypTool\index{CrypTool} v1.3 you also can try brute-force attacks
    of modern symmetric algorithms 
    (using the menu {\bf Analysis \textbackslash{} Ciphertext-Only}): 
    to achieve a result in an appropriate time with a single PC you should 
    mark not more than 20 bit of the key as unknown.
}.

@@

It is well-known, that the "old" standard algorithm DES with a fixed key length of 56 bit is no more secure: this was demonstrated already in January 1999 by the Electronic Frontier Foundation (EFF). With their specialized computer Deep Crack they cracked a DES encrypted message within less than a day\footnote{\href{http://www.rsasecurity.com/rsalabs/challenges/des3/index.html}{\tt http://www.rsasecurity.com/rsalabs/challenges/des3/index.html}}.

@@

\bibitem[Schmeh2003]{Schmeh2003}  \index{Schmeh 2003}
        Klaus Schmeh, \\
        {\em Cryptography and Public Key Infrastructures on the Internet},\\ 
        John Wiley \& Sons Ltd., Chichester 2003. \\
        A considerable, up-to-date, easy to read book, which also 
        considers practical problems like standardisation or
        real existing software.

>>>>

The purpose of encryption \index{Encryption} is to change data in such a way
that only an authorised recipient is able to reconstruct the plaintext. This
allows us to transmit data without worrying about it getting into unauthorised
hands. Authorised recipients possess a piece of secret information -- called the
key -- which allows them to decrypt the data while it remains hidden from
everyone else.\par \vskip + 3pt

One encryption procedure has been mathematically proved to be secure, the {\em
One Time Pad}\index{One ­Time ­Pad}. However, this procedure has several
practical disadvantages (the key used must be randomly selected and must be at
least as long as the message being protected), which means that it is hardly
used except in closed environments such as for the hot wire between Moscow and
Washington.\par \vskip + 3pt

@@

The book of Bruce Schneier \cite{Schneier1996cm} offers a very good overview of
the different algorithms. We basically distinguish between symmetric and
asymmetric encryption procedures.

@@

In their 2001-paper Ferguson, Schroeppel and Whiting \cite{Ferguson2001}
presented a new method of symmetric codes cryptanalysis: They described AES with
a closed formula (in the form of a continued fraction) which was possible
because of the "relatively" clear structure of AES. This formula consists of
around 1000 trillion terms of a sum - so it does not help concrete practical
cryptanalysis. Nevertheless -curiosity in the academic community was awakened.
It was already known, that the 128-bit AES could be described as an
over-determined system of about 8000 quadratic equations (over an algebraic
number field) with about 1600 variables (some of them are the bits of the wanted
key) -- equation systems of that size are in practice not solvable. This special
equation system is relatively sparse, so only very few of the quadratic terms
(there are about 1,280,000 are possible quadratic terms in total) appear in the
equation system.

The mathematicians Courtois and Pieprzyk \cite{Courtois2002} published a paper
in 2002, which got a great deal of attention amongst the crypto community: The
pair had further developed the XL-method (eXtended Linearization), introduced at
Eurocrypt 2000 by Shamir et al., to create the so called XSL-method (eXtended
Sparse Linearization). The XL-method is a heuristic technique, which in some
cases manages to solve big non-linear equation systems and which was till then
used to analyze an asymmetric algorithm (HFE).  The innovation of Courois and
Pieprzyk was, to apply the XL-method on symmetric codes: the XSL-method can be
applied to very specific equation systems. A 256-bit AES could be attacked in
roughly $2^{230}$ steps. This is still a purely academic attack, but also a
direction pointer for a complete class of block ciphers. The major problem with
this attack is that until now nobody has worked out, under what conditions it is
successful: the authors specify in their paper necessary conditions, but it is
not known, which conditions are sufficient.  There are two very new aspects of
this attack: firstly this attack is not based on statistics but on algebra. So
attacks seem to be possible, where only very small amounts of cipher text are
available. Secondly the security of a product-algorithm does not exponentially
increase with the number of rounds.

@@

The discussion is very controversial at the moment: Don Coppersmith (one of the
inventors of DES) for example queries the practicability of the attack because
XLS would provide no solution for AES \cite{Coppersmith2002}. This implies that
then the optimization of Murphy and Robshaw \cite{Robshaw2002b} would not work.

@@

Brute-force (exhaustive search, trial-and-error) means to completely examine all keys of the key space: so no special analysis methods have to be used. Instead, the cipher text is decrypted with all possible keys and for each resulting text it is checked, whether this is a meaningful clear text. A key length of 64 bit means at most $2^{64}$ = 18,446,744,073,709,551,616 or about 18 trillion (GB) / 18 quintillion (US)  keys to check\index{CrypTool}%
\footnote{%
    With CrypTool\index{CrypTool} v1.3 you can also try brute-force attacks
    of modern symmetric algorithms 
    (using the menu {\bf Analysis \textbackslash{} Ciphertext-Only}): 
    to achieve a result in an appropriate time with a single PC you should 
    mark not more than 20 bit of the key as unknown.
}.

@@

It is well-known, that the ``old'' standard algorithm DES with a fixed key length of 56 bit is no more secure: this was demonstrated already in January 1999 by the Electronic Frontier Foundation (EFF). With their specialized computer Deep Crack they cracked a DES encrypted message within less than a day\footnote{\href{http://www.rsasecurity.com/rsalabs/challenges/des3/index.html}{\tt http://www.rsasecurity.com/rsalabs/challenges/des3/index.html}}.

@@

\bibitem[Schmeh2003]{Schmeh2003}  \index{Schmeh 2003}
        Klaus Schmeh, \\
        {\em Cryptography and Public Key Infrastructures on the Internet},\\ 
        John Wiley \& Sons Ltd., Chichester 2003. \\
        A considerable, up-to-date, easy to read book, which also 
        considers practical problems such as standardisation or
        real existing software.

### 2003-04-07 script/en/chapters/digitalsignatures.tex
richard's comments

In detail, a \index{Signature procedure} {\em Signature procedure} looks like
this: \\ Senders use their message and secret key to calculate the digital
signature for the message. Compared to hand-written signatures, therefore,
digital signatures have the advantage that they also depend on the document to
be signed. Signatures from one and the same participant are different unless the
signed documents are completely identical. Even inserting a blank in the text
would lead to a different signature. The recipient of the message would
therefore detect any injury to the message integrity as this would mean that the
signature no longer matches the document and is shown to be incorrect when
verified.

@@

Some digtal signature schemes are based on asymmetric \emph{encryption}
procedures, the most prominent example beeing the RSA system, which can be
used for signing by performing the private key operation on the hash value
of the document to be signed.

@@

The RSA signature $S$ for a message $M$ is created by performing the private
key operation:
$$ S \equiv M^d \Mod{N} $$
In order to verify, the corresponding public key operation is performed on
the signature $S$ and the result is compared with message $M$:
$$ S^e \equiv (M^d)^e \equiv (M^e)^d \equiv M \Mod{N}$$
If the result matches the message $M$, then the signature is accepted by the
verifyer, otherwise the message has been tampered with, or was never signed
by the holder of $d$.

As explained above, signatures are not performed on the message itself, but
on a cryptographic hash value of the message. To preclude certain attacks
on the signature procdedure (alone or in combination with encryption) it is
necessary to format the hash value before doing the exponentiation, as
described in the PKCS\#1 (Public Key Cryptography Standard \#1
\cite{PKCS1}). The fact that this standard had to be revised recently, after
being in use for several years, can serve as an example how difficult it is
to get the details of cryptography right.

@@

In August of 1991, the U.S. National Institute of Standards and Technology
(NIST\index{NIST}) proposed a digital signature algorithm (DSA), which was adopted as
a U.S. Federal Information Processing Standard (FIPS 186 \cite{FIPS186})
subsequently.

@@

While DSA was specifically designed, such that it can be exported from
countries regulating export of encryption soft and hardware (like the U.S.\ 
at the time when it was specified), it has been noted
\cite[p.~490]{Schneier1996ds}, that the operations involved in DSA can be
used to emulate RSA and ElGamal encryption.

@@

Charlie can thus listen in on communication between Alice and Bob and change the
exchanged messages without them noticing. The attack also works if Charlie only
has one pair of keys.

>>>>

In detail, a \index{Signature procedure} {\em Signature procedure} looks like
this: \\ Senders use their message and secret key to calculate the digital
signature for the message. Compared to hand-written signatures, digital
signatures therfore have the advantage that they also depend on the document to
be signed. Signatures from one and the same participant are different unless the
signed documents are completely identical. Even inserting a blank in the text
would lead to a different signature. The recipient of the message would
therefore detect any injury to the message integrity as this would mean that the
signature no longer matches the document and is shown to be incorrect when
verified.

@@

Some digital signature schemes are based on asymmetric \emph{encryption}
procedures, the most prominent example beeing the RSA system, which can be
used for signing by performing the private key operation on the hash value
of the document to be signed.

@@

The RSA signature $S$ for a message $M$ is created by performing the private
key operation:
$$ S \equiv M^d \Mod{N} $$
In order to verify, the corresponding public key operation is performed on
the signature $S$ and the result is compared with message $M$:
$$ S^e \equiv (M^d)^e \equiv (M^e)^d \equiv M \Mod{N}$$
If the result matches the message $M$, then the signature is accepted by the
verifier, otherwise the message has been tampered with, or was never signed
by the holder of $d$.

As explained above, signatures are not performed on the message itself, but
on a cryptographic hash value of the message. To prevent certain attacks
on the signature procedure (alone or in combination with encryption) it is
necessary to format the hash value before doing the exponentiation, as
described in the PKCS\#1 (Public Key Cryptography Standard \#1
\cite{PKCS1}). The fact that this standard had to be revised recently, after
being in use for several years, can serve as an example of how difficult it is
to get the details of cryptography right.

@@

In August of 1991, the U.S. National Institute of Standards and Technology
(NIST\index{NIST}) proposed a digital signature algorithm (DSA), which was
subsequently adopted as a U.S. Federal Information Processing Standard (FIPS 186
\cite{FIPS186}).

@@

While DSA was specifically designed, so that it can be exported from
countries regulating export of encryption soft and hardware (like the U.S.\ 
at the time when it was specified), it has been noted
\cite[p.~490]{Schneier1996ds}, that the operations involved in DSA can be
used to emulate RSA and ElGamal encryption.

@@

In this way Charlie can listen in on communication between Alice and Bob and
change the exchanged messages without them noticing. The attack will also work
if Charlie only has one pair of keys.

### 2003-04-07 script/en/chapters/introduction.tex
richard's comments

Starting in the year 2000 this script became a part of the 
CrypTool\index{CrypTool} package. It should accomplish the program 
CrypTool by explaining some mathematical topics in more details, 
but still in a way which is easy to understand.

In order to also enable developers/authors to work together independently 
the topics have been split up and for each topic an extra chapter was 
written readable on its own. The later editorial work in TeX added 
cross linkages between different sections and footnotes describing where you
can find the according 
functions within the CrypTool\index{CrypTool} program. Naturally 
there are much more interesting topics in mathematics and cryptography 
which could be more expanded -- therefore this is only one of many
ways to do it.

\vspace{12pt}
Rapid spread of the Internet has also lead to an intensified research 
in the technologies involved, especially within the area of cryptography 
where a good deal of new knowledge came up.

@@

Chapter 6 of this script was also enhanced: now we explain in more details how elliptic curves are defined over different number fields.

\vspace{12pt}
The first time the script was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been extended and updated with each 
new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03 and now 1.3.04).

I'd be more than happy if this keeps on going also in the further 
open source versions of CrypTool\index{CrypTool} (they will be delivered by the University of Darmstadt).

I am deeply grateful to all the people helping with their impressive
committment to make this project successful and wide-spreading.

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding for this modern but 
also very ancient topic.
\\

@@

This script is delivered together with the program CrypTool\index{CrypTool}. \par \vskip + 3pt

Because the articles in this script are largely self-contained, this script
can also be read independently of CrypTool\index{CrypTool}.

@@

CrypTool\index{CrypTool} has often been used for 
education in companies and teaching at school and universities, and
moreover several universities are helping to further develop the project.
\par \vskip + 15pt

@@

At this point I'd like to thank explicitely 3 people who especially 
contributed to CrypTool\index{CrypTool}. Without their talents and engagement 
CrypTool would not be what it is today:
\vspace{-7pt}
\begin{itemize}
   \item Mr. Henrik Koy
   \item Mr. J\"org-Cornelius Schneider and
   \item Dr. Peer Wichmann.
\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

>>>>

Starting in the year 2000 this script became a part of the 
CrypTool\index{CrypTool} package. It is designed to accompany the program 
CrypTool by explaining some mathematical topics in more detail, 
but still in a way which is easy to understand.

In order to also enable developers/authors to work together independently 
the topics have been split up and for each topic an extra chapter has been 
written which an be read on its own. The later editorial work in TeX added 
cross linkages between different sections and footnotes describing where you
can find the according 
functions within the CrypTool\index{CrypTool} program. Naturally 
there are much more interesting topics in mathematics and cryptography 
which could be discussed in greater depth -- therefore this is only one of many
ways to do it.

\vspace{12pt}
Rapid spread of the Internet has also lead to intensified research in the
technologies involved, especially within the area of cryptography where a good
deal of new knowledge has arisen.

@@

Chapter 6 of this script has also been enhanced: now we explain in greater
detail how elliptic curves are defined over different number fields.

\vspace{12pt}
The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in every 
new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03 and now 1.3.04).

I'd be more than happy if this also continues in the further open-source
versions of CrypTool\index{CrypTool} (they will be delivered by the University
of Darmstadt).

I am deeply grateful to all the people helping with their impressive
commitment who have made this global project so successful.

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\\

@@

This document is delivered together with the program CrypTool\index{CrypTool}. \par \vskip + 3pt

Because the articles in this script are largely self-contained, this text
can also be read independently of CrypTool\index{CrypTool}.

Chapters 4 and 6 might require a deeper knowledge in mathematics, while the
other chapters should be understandable with a school leaving certificate.

@@

CrypTool\index{CrypTool} is currently been used for 
training in companies and teaching at school and universities, and
moreover several universities are helping to further develop the project.
\par \vskip + 15pt

@@

At this point I'd like to thank explicitly 3 people who especially 
contributed to CrypTool\index{CrypTool}. Without their talents and engagement 
CrypTool would not be what it is today:
\vspace{-7pt}
\begin{itemize}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider and
   \item Dr.\ Peer Wichmann.
\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

### 2003-04-07 script/en/chapters/moderncryptography.tex
richard's comments

    \item The class \textbf{NP}: The definition of this class looks not at the 
time required to solve a problem, but rather at the time required to verify a 
given solution. The class \textbf{NP} consists of those problems for which a 
given solution can be verified in a polynomial amount of time. Hereby, the term 
\textbf{NP} ``non-deterministic'' means polynomial and is based on a 
calculation model, i.e. on a computer that only exists in theory and can 
``guess'' correct solutions non-deterministically then verify them in 
polynomial time.

@@

Two 0-1 knapsack problems  $ K(a_1, \dots, a_n;g) $   and  $ K(a'_1, \dots, 
a'_n;g') $  are called congruent if two \index{Co-prime} co-prime numbers $ w $ 
and $ m $ exist such that
\begin{enumerate}
    \item $ m > \max \{ \sum_{i=1}^n a_i , \sum_{i=1}^n a'_i \}, $

@@

{\bf Comment:}
Congruent 0-1 knapsack problems have the same solutions.
No quick algorithm is known for clarifying the question whether two 0-1 knapsack 
problems are congruent.

@@

In 1982, \index{Shamir Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial time without solving the general knapsack 
problem. Len \index{Adleman Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by a perpetrator.

>>>>

		\item The class \textbf{NP}: The definition of this class doesn't look at
		the time required to solve a problem, but rather at the time required to
		verify a given solution. The class \textbf{NP} consists of those problems
		for which a given solution can be verified in a polynomial amount of time.
		Hereby, the term \textbf{NP} ``non-deterministic'' means polynomial and is
		based on a calculation model, i.e. on a computer that only exists in theory
		and can ``guess'' correct solutions non-deterministically then verify them
		in polynomial time.

@@

Two 0-1 knapsack problems  $ K(a_1, \dots, a_n;g) $   and  $ K(a'_1, \dots, 
a'_n;g') $  are called congruent if two \index{Co-prime} co-prime numbers $ w $ 
and $ m $ exist in such a way that
\begin{enumerate}
    \item $ m > \max \{ \sum_{i=1}^n a_i , \sum_{i=1}^n a'_i \}, $

@@

{\bf Comment:}
Congruent 0-1 knapsack problems have the same solutions.
No quick algorithm is known for clarifying the question as to whether two 0-1
knapsack problems are congruent.

@@

In 1982, \index{Shamir Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial time without solving the general knapsack 
problem. Len \index{Adleman Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by an evesdropper.
